### 2022-12-02 definitions.tex
details

\problemx{Resilience problem for WSTS}
{A state $s$ of a WSTS $(S,\rightarrow, \leq)$, an upward-closed set $U$ with a given basis, a decidable downward-closed set $D$.}
{$\exists k \geq 0 ~ \forall s' \in D ~ (s \rightarrow^* s') \implies \exists s'' \in U ~ s' \rightarrow^{\leq k} s''$ ?\newline}

\alain{examiner les cas I,J un élement, cloture, tout, ...}

@@

@@

\begin{proposition}
{\sc $k$-resilience}, hence {\sc resilience}, is undecidable for effective WSTS with strong upward compatibility.
\end{proposition}

>>>>

\problemx{bounded Resilience problem for WSTS}
{A state $s$ of a WSTS $(S,\rightarrow, \leq)$, an upward-closed set $U$ with a given basis, a decidable downward-closed set $D$.}
{$\exists k \geq 0 ~ \forall s' \in D ~ (s \rightarrow^* s') \implies \exists s'' \in U ~ s' \rightarrow^{\leq k} s''$ ?\newline}

\problemx{Resilience problem for WSTS}
{A state $s$ of a WSTS $(S,\rightarrow, \leq)$, an upward-closed set $U$ with a given basis, a decidable downward-closed set $D$.}
{$ ~ \forall s' \in D ~ (s \rightarrow^* s') \implies \exists s'' \in U ~ s' \rightarrow^{*} s''$ ?\newline}

\alain{examiner les cas I,J un élement, cloture, tout, clos par le bas et par le haut,... ...}

@@

\alain{regarder les modèles aut à pile...}

@@

\begin{proposition}
{\sc $k$-resilience}, hence {\sc resilience}, is undecidable for effective WSTS with strong upward compatibility ?
\end{proposition}
